I don't know, are you sure we want to do this?\ Sea level adaptation decisions under uncertainty

### 2016-10-29 submission/paper.tex
Updated details about data cleaning for Bergen

\subsection{Data {\color{blue} (PG)}}
Historical global mean temperature is obtained from \citet{giss}. Climate projections of global mean temperature are from the fifth climate model intercomparison project, CMIP5 \citep{cmip5}. The global mean sea level series is obtained from \citet{csiro}. We use local tide gauge data from the Permanent Service for Mean Sea Level, UK, which is the worldwide repository for national sea level data. Glacial isostatic adjustment for Bergen is obtained from \citet{Simpson2014}.

Figure \ref{fig:obs} shows uncorrected and corrected Bergen sea level data, and the relationship between the corrected Bergen data and the global sea level data. The time series regression uses an ARMA(1,1)-model \citep{boxjenkins}. 
\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergenfit.png}
\caption{ The left figure shows raw (black)and gia-corrected (red) sea level data from Bergen, The right figure relates the gia-corrected Bergen sea level to the global sea level series of \citet{csiro}. The straight line is the time series regression line.}
\label{fig:obs}
\end{center}
\end{figure}

Figure \ref{fig:ci} shows the simultaneous 90 \% confidence region for Bergen sea level rise relative to 1999.
\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergen_ci.png}
\caption{Simultaneous 90\% confidence set (thick black lines) for Bergen sea level projections for the years 2000-2100 using RCP8.5. The sea level data are shown in blue and end in 2015. The thin red lines are the projections without uncertainty based on each of the climate models. The dashed purple lines connect pointwise confidence intervals for each year. }
\label{fig:ci}
\end{center}
\end{figure}

@@

>>>>

\subsection{Data {\color{blue} (PG)}}
The historical global mean temperature series is obtained from \citet{giss}. Climate projections of global mean temperature are from the fifth climate model intercomparison project, CMIP5 \citep{cmip5}. The global mean sea level series is obtained from \citet{csiro}. We use local tide gauge data from the Permanent Service for Mean Sea Level, UK, which is the worldwide repository for national sea level data. Glacial isostatic adjustment for Bergen is obtained from \citet{Simpson2014}.

The Bergen monthly series is missing data for 62 months, including all of the years 1942--43. To deal with occasional short stretches of missing data (most one or two months) we use median polish replacement \citep{medpol}. For the years 1942-43, we use use the average difference between Bergen and the average of all other Norwegian stations in 1940 and 1943 to estimate values for 1941 and 1942, using the average of all other stations corrected by the average difference.

@@

\subsection{Sea level rise in Bergen}

Figure \ref{fig:obs} shows uncorrected and corrected Bergen sea level data, and the relationship between the corrected Bergen data and the global sea level data. The time series regression uses an ARMA(1,1)-model \citep{boxjenkins}, with AR parameter 0.82 (0.13), and MA parameter --0.61 (0.17). The regression slope is 1.30 (0.12).
\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergenfit.png}
\caption{ The left figure shows raw (black)and gia-corrected (red) sea level data from Bergen, The right figure relates the gia-corrected Bergen sea level to the global sea level series of \citet{csiro}. The straight line is the time series regression line.}
\label{fig:obs}
\end{center}
\end{figure}

For the relationship between global annual mean temperature and global annual mean sea level rise we use the results from \citet{Bolin2014a}. Figure \ref{fig:ci} shows the simultaneous 90 \% confidence region for Bergen sea level rise relative to 1999 under scenario RCP 8.5, which is the scenario Norwegian authorities recommend for planning purposes.
\begin{figure}
\begin{center}
\includegraphics[width=39pc]{bergen_ci.png}
\caption{Simultaneous 90\% confidence set (thick black lines) for Bergen sea level projections for the years 2000-2100 using RCP8.5. The sea level data are shown in blue and end in 2015. The thin red lines are the projections without uncertainty based on each of the climate models. The dashed purple lines connect pointwise confidence intervals for each year. }
\label{fig:ci}
\end{center}
\end{figure}
